Behavior Driven Development in Haskell

### 2012-05-23 paper.tex
writing solution.

\noindent Some Haskellers like this kind of equations and dislike to write it with the example annotation as follow:

@@

talk about doctest.

talk about the {\tt prop>} syntax.

talk about how to specify non-boolean properties.

>>>>

\noindent Some Haskellers like this kind of equations and dislike to write it with the example annotation as follows:

@@

To execute examples in haddock annotations, we introduced {\tt doctest} from Python community and implemented it in Haskell.

TBD: talk about exception.

To specify properties in haddock annotations, we propose a new syntax. In this paper, we use the {\tt prop>} prefix. We can write the boolean equation as follows:

\begin{quote}
\begin{verbatim}
prop> Data.Map.null (empty) == True
\end{verbatim}
\end{quote}

\noindent talk about how to specify non-boolean properties.

\begin{quote}
\begin{verbatim}
prop> \xs -> sort xs == sort (sort (xs::[Int]))
\end{verbatim}
\end{quote}

\noindent talk about open lambda term.

\begin{quote}
\begin{verbatim}
prop> sort xs == sort (sort (xs::[Int]))
\end{verbatim}
\end{quote}
